Project Setup

### 2024-09-07 setup.qmd
Use OSC link for FAIR data workshop and remove note about file.path()
Windows users are already encouraged to use
forward slashes rather than backward slashes,
so using file.path() probably doesn't add
too much value.

A human-readable data dictionary is necessary for making one's research reproducible and the example we provided demonstrates only the bare minimum. A full data documentation including measurement instruments, sampling procedures, appropriate weighting, contact information, and more information about the study can be created with the R package [`pointblank`](https://rstudio.github.io/pointblank/articles/INFO-1.html). And one could go even further by making the information machine-readable in a standardized way. We provide an optional example of that in @nte-frictionless. If you want to learn more about the sharing of research data, have a look at the tutorial "[FAIR Data management](https://github.com/MPDL/FAIR-Data-Management)".

@@

- __Use project-relative paths.__ When you refer to a file within your project, write paths relative to your project root. For example, don't write `C:\Users\Public\Documents\my_project\images\result.png`, instead write `images\result.png`.^[In R, use `file.path()` for a platform-independent way to concatenate folders to build a path.]

>>>>

A human-readable data dictionary is necessary for making one's research reproducible and the example we provided demonstrates only the bare minimum. A full data documentation including measurement instruments, sampling procedures, appropriate weighting, contact information, and more information about the study can be created with the R package [`pointblank`](https://rstudio.github.io/pointblank/articles/INFO-1.html). And one could go even further by making the information machine-readable in a standardized way. We provide an optional example of that in @nte-frictionless. If you want to learn more about the sharing of research data, have a look at the tutorial "[FAIR Data management](https://lmu-osc.github.io/FAIR-Data-Management/)".

@@

- __Use project-relative paths.__ When you refer to a file within your project, write paths relative to your project root. For example, don't write `C:/Users/Public/Documents/my_project/images/result.png`, instead write `images/result.png`.
